---
title: "ATAC-seq Differential Accessibility Analysis" 
author: "Department of Biostat and Bioinfo"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: readable
    toc: true
    toc_float: true
    df_print: paged
params:
    date: !r Sys.Date()
    btable: "bin.table.filename"
    c1name: "c1name"
    c2name: "c2name"
    metafile: "meta.filename"
    fdr: 0.05
    log2fc: 0.58
    gmtfolder: "GMT folder path"
    cistrome: "cistrome db path"
---

```{r configuration, include = TRUE, echo=TRUE }
# input file
bincount.table <- params$btable

# condition names
condition1name <- params$c1name
condition2name <- params$c2name
metafile <- params$metafile

# DAR cutoff settings
fdr.cutoff <- as.numeric( params$fdr )
log2fc.cutoff <- as.numeric( params$log2fc )

# other annotations
gmtfolder <- as.character( params$gmtfolder )
cistrome.gigglepath <- as.character( params$cistrome )
cistrome.annotation <- paste0(cistrome.gigglepath,"/CistromeDB.sample.annotation.txt")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# settings
library(tximport)
library(DESeq2)
library(ggplot2)
library(pcaExplorer)
library(RColorBrewer)
library(pheatmap)
library(scales)
library(ggrepel)
library(plotly)
library(UpSetR)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
library(org.Mm.eg.db)
library(ChIPseeker)
library(clusterProfiler)
library(patchwork)

options(stringsAsFactors=F)

# some customized functions

# savePeak function
savePeak <- function( data, filename ) {
  peak.name <- rownames(data)
  peak.score <- as.integer(-10*log10(data$padj))
  peak.location <- gsub(":|-","\t",data$location)
  peak.content <- paste(peak.location, peak.name, peak.score, rep(".",length(peak.name)), sep="\t")
  write(peak.content, file = filename)
}

# giggle function to run against cistromeDB
RunGiggle.Cistrome <- function(peakbed, giggle.path, organism, antFile){
  outputBed = peakbed
  cmd <- paste0("sort --buffer-size 2G -k1,1 -k2,2n -k3,3n ", outputBed, " | cut -f 1,2,3 | bgzip -c > ", outputBed, ".bed.gz")
  system(cmd)
  cmd <- paste0("giggle search -g 2700000000 -i ", giggle.path, "/giggle.", organism, " -q ", outputBed, ".bed.gz -s > ", outputBed, ".result.xls")
  system(cmd)
  resultDf <- read.table(paste0(outputBed, ".result.xls"), sep="\t", row.names=NULL, comment.char="", stringsAsFactors =  FALSE)
  resultDf <- resultDf[,-9]
  colnames(resultDf) <- c("file", "file_size", "overlaps", "odds_ratio", "fishers_two_tail", "fishers_left_tail", "fishers_right_tail", "combo_score")
  resultDf <- resultDf[resultDf$overlaps>0,] #at least some overlap
  resultDf <- resultDf[resultDf$"odds_ratio">1,] # at least some enrichment over random
  rownames(resultDf) <- sapply(strsplit(resultDf$file, "/"), function(x) return(gsub("_5foldPeak.bed.gz", "", rev(x)[1])))
  resultDf <- resultDf[,c("file_size", "overlaps", "combo_score", "odds_ratio", "fishers_right_tail")]
  targetDf <- merge(resultDf, antFile, by.x=0, by.y=0)
  colnames(targetDf) <- c("sample_id", "sample_peak_number", "overlap_peak_number", "giggle_score", "odds_ratio", "fisher_right_tail", "GSM_id", "species", "factor", "cell_line", "cell_type", "tissue", "disease")

  targetDf$biological_resource <- apply(targetDf, 1, function(x) return(paste0(x[7:10], collapse=";")))
  targetDf$labels <- paste0(targetDf$"cell_line",":",targetDf$"factor")
  targetDf$fisher_right_tail <- -log10(targetDf$"fisher_right_tail")
  targetDf$"odds_ratio" <- log10(targetDf$"odds_ratio")  
  
  targetDf <- targetDf[, c("sample_id", "GSM_id", "species", "factor", "biological_resource", "labels", "giggle_score", "odds_ratio", "fisher_right_tail", "sample_peak_number", "overlap_peak_number")]
  targetDf <- targetDf[order(-targetDf$giggle_score), ]
  targetDf <- targetDf[!duplicated(targetDf$factor), ]
  write.table(targetDf, paste0(outputBed, ".giggle.res.tfs.txt"), sep="\t", quote=FALSE, row.names=FALSE)
  cmd <- paste0("rm ", outputBed, ".bed.gz")
  system(cmd)
  cmd <- paste0("rm ", outputBed, ".result.xls")
  system(cmd)
  return(targetDf)
}

# giggle function to run on ENCODE cCRE (human)
RunGiggle.cCRE <- function(peakbed, giggle.ccre.path){
  outputBed = peakbed
  # bgzip
  cmd <- paste0("sort --buffer-size 2G -k1,1 -k2,2n -k3,3n ", outputBed, " | cut -f 1,2,3 | bgzip -c > ", outputBed, ".bed.gz")
  system(cmd)
  
  # get overlaps in BED
  cmd <- paste0("giggle search -g 2700000000 -i ", giggle.ccre.path, " -q ", outputBed, ".bed.gz  -f pELS -o -v | perl -e '$_=<>;chomp;s/^##//;$p=$_;@id=();while(<>){if(/^##/){if(@id){print $p,\"\\t\",join(\",\",@id),\"\\n\";}chomp;s/^##//;$p=$_;@id=();}else{@_=split;push @id,$_[3];}}if(@id){print $p,\"\\t\",join(\",\",@id),\"\\n\";}' > ", outputBed, ".result.pELS.bed" )
  system(cmd)
  cmd <- paste0("giggle search -g 2700000000 -i ", giggle.ccre.path, " -q ", outputBed, ".bed.gz  -f dELS -o -v | perl -e '$_=<>;chomp;s/^##//;$p=$_;@id=();while(<>){if(/^##/){if(@id){print $p,\"\\t\",join(\",\",@id),\"\\n\";}chomp;s/^##//;$p=$_;@id=();}else{@_=split;push @id,$_[3];}}if(@id){print $p,\"\\t\",join(\",\",@id),\"\\n\";}' > ", outputBed, ".result.dELS.bed" )
  system(cmd)
  
  # get summary
  cmd <- paste0("giggle search -g 2700000000 -i ", giggle.ccre.path, " -q ", outputBed, ".bed.gz -s > ", outputBed, ".result.tsv")
  system(cmd)
  resultDf <- read.table(paste0(outputBed, ".result.tsv"), sep="\t", row.names=, comment.char="#", stringsAsFactors =  FALSE)
  resultDf <- resultDf[,-9]
  colnames(resultDf) <- c("class","file_size","overlaps","odds_ratio","fishers_two_tail","fishers_left_tail","fishers_right_tail","combo_score")
  
  cmd <- paste0("rm ", outputBed, ".bed.gz")
  system(cmd)
  cmd <- paste0("rm ", outputBed, ".result.tsv")
  system(cmd)
  resultDf$class <- gsub("encodeCcre/encodeCcre-","",resultDf$class)
  resultDf$class <- gsub(".bed.gz","",resultDf$class)
  return(resultDf)
}

# merge bins into region
MergeBin <- function( binbed, regionbed ) {
  cmd <- paste0( "bedtools sort -i ", binbed, " | bedtools merge -i - -c 5 -o max > ", regionbed )
  system(cmd)
}

```

```{r config.exp, include=FALSE}
# distance cutoff for chipseeker to link dar to gene
dar2gene.distance.cutoff <- 10000

# parameters for enrichr/clusterprofiler
cp.pvalueCutoff = 0.05
cp.pAdjustMethod = "BH"
cp.minGSSize = 5
cp.maxGSSize = 500
cp.qvalueCutoff = 0.2

# output dar bed
dbin.plus.vs.minus.all.bed <- "dbin.all.bed"
dbin.plus.vs.minus.open.bed <- "dbin.open.bed"
dbin.plus.vs.minus.close.bed <- "dbin.close.bed"

dar.plus.vs.minus.open.bed <- "dar.open.bed"
dar.plus.vs.minus.close.bed <- "dar.close.bed"

# saved RDS files
ddsfile <- "dds.rds"
vsdfile <- "vsd.rds"
resultfile <- "result.rds"

```

```{r loaddata, include=FALSE, echo=TRUE}
# meta information
meta <- read.table(metafile,head=T,row.names=1)
meta$Replicate <- as.factor(meta$Replicate)
meta$Group <- as.factor(meta$Group)

```

```{r}
# load cistrome annotation
ant <- read.csv(cistrome.annotation, sep="\t", row.names=1, stringsAsFactors = FALSE)

```

```{r}
# load bincount matrix values
d <- as.matrix(read.csv(bincount.table,sep="\t",row.names="bin_id",check.names = FALSE))
## extract peak information
peak.info<-data.frame(d[,c("pos","chr","start","end")])
colnames(peak.info) <- "pos"
## remove peak information from d, set mode
d <- d[,-c(1,2,3,4)]
mode(d) <- "integer"
## make sure orders in meta and d are the same
meta <- meta[order(rownames(meta)),]
d <- d[,order(colnames(d))]
```

```{r load.gmt, echo=FALSE}
# load gmt files for enricher/clusterprofiler
# hall mark
hgmtfile <- paste0(gmtfolder, "/mh.all.v0.3.entrez.gmt")
hgene <- read.gmt(hgmtfile)

# ontology
gogmtfile <- paste0(gmtfolder, "/m5.all.v0.3.entrez.gmt")
gogene <- read.gmt(gogmtfile)

# oncogenic signature
oncogmtfile <- paste0(gmtfolder, "/m4.all.v0.3.entrez.gmt")
oncogene <- read.gmt(oncogmtfile)

# TF targets Signatures
tftgmtfile <- paste0(gmtfolder, "/m3.all.v0.3.entrez.gmt")
tftgene <- read.gmt(tftgmtfile)

# Canonical pathways
pathgmtfile <- paste0(gmtfolder, "/m2.cp.v0.3.entrez.gmt")
pathgene <- read.gmt(pathgmtfile)
```

# Intro

```{r deseq2run, include=FALSE, echo=TRUE}
# DESeq2
dds<-DESeqDataSetFromMatrix(d,colData=meta,design=~Group)
dds<-DESeq(dds,betaPrior=F)

vsd<-varianceStabilizingTransformation(dds,blind=FALSE)
```

The aim for this analysis is to identify the chromatin accessibility changes, in terms of the Differentially Accessible Regions (DARs) from ATAC-seq, with `r condition2name` against with `r condition1name`. After calling peaks from ATAC-seq of the two conditions "`r condition1name`" and "`r condition2name`", we merged all peaks and keep only those genomic regions that can be detected as 'peak' in at least two replicates as the region of interest. We have `r length(rownames(dds))` regions of interest peaks across all samples. Then we generated read counts for each condition and each replicate in each region of interest. The count table is further processed through DESeq2 to call the DARs. Normalization is through VST -- Variance Stabilizing Transformation. 

## PCA 

A PCA analysis is performed on normalized data. We use PCA to explore the potential clustering in the samples. We can see the the Principal Component #1, which explains 94% of the variance within samples, is related to condition 2 against condition 1.

```{r PCA, dev="png",dpi=300,fig.height=4,fig.width=6,echo=F,message=F}
p<-plotPCA(vsd,intgroup=c("Group"), returnData=T)
percentVar <- round(100 * attr(p, "percentVar"))
muc1.bt549.pcaplot <- ggplot(p, aes(PC1, PC2, color=Group)) +
  geom_point(size=3) +
  xlab(paste0("PC1: ",percentVar[1],"% variance")) +
  ylab(paste0("PC2: ",percentVar[2],"% variance")) + 
  labs(colour="Group")
muc1.bt549.pcaplot
```

## Correlation heatmap

Correlation analysis is performed on all counts data among all samples. Hierarchical clustering is based on correlation values among samples. Each sample is annotated with corresponding conditin and replicate. We could see the same conclusion as in our PCA analysis. 

```{r CorHeatmap, dev="png",dpi=300,fig.height=5,fig.width=7,echo=F,message=F}
sampleDists<-dist(t(assay(vsd)))
sampleDistMatrix<-as.matrix(sampleDists)
colnames(sampleDistMatrix)<-NULL
colors<-colorRampPalette(rev(brewer.pal(9,"Blues")))(255)
pheatmap(sampleDistMatrix,clustering_distance_rows=sampleDists,clustering_distance_cols=sampleDists,col=colors,annotation_row = meta[,c("Group","Replicate")], fontsize_row = 6 )
```

# DAR analysis

DARs are called by using log2 foldchange cutoff of `r log2fc.cutoff` and FDR cutoff of `r fdr.cutoff`. We specifically called the DARs between `r condition1name` and `r condition2name`.

## Summary of called differential bins
```{r CallDbins, echo=FALSE}
dbins.plus.vs.minus <- results(dds,contrast=c("Group",condition2name,condition1name))

dbins.plus.vs.minus.df <- data.frame(location=peak.info[rownames(dbins.plus.vs.minus[order(dbins.plus.vs.minus$padj),]),"pos"], dbins.plus.vs.minus[order(dbins.plus.vs.minus$padj),c("baseMean","log2FoldChange","pvalue","padj")])

dbins.plus.vs.minus.filtered <- dbins.plus.vs.minus.df[!is.na(dbins.plus.vs.minus.df$padj) & dbins.plus.vs.minus.df$padj<=fdr.cutoff & abs(dbins.plus.vs.minus.df$log2FoldChange)>=log2fc.cutoff,]
```

```{r save, echo=F}
saveRDS(dds,ddsfile)
saveRDS(vsd,vsdfile)
saveRDS(dbins.plus.vs.minus, resultfile)

savePeak(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,],dbin.plus.vs.minus.open.bed)
savePeak(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,],dbin.plus.vs.minus.close.bed)
```

We have `r dim(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,])[1]` differential bins openning up and `r dim(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,])[1]` differential bins closing down. The differential bins are saved in `r dbin.plus.vs.minus.open.bed`

## MA-plot and volcano plot

MA-plot and volcano plot can be seen below. Note that these plots are based on 'bins'.

### `r condition2name` vs `r condition1name`

```{r MAvolcano1, dev="png",dpi=300,fig.height=5,fig.width=10,echo=F,message=F }
par(mfcol=c(1,2))
plot(log10(dbins.plus.vs.minus$baseMean),dbins.plus.vs.minus$log2FoldChange,pch=20,cex=0.5,ylab=paste0("log2 foldchange(",condition2name,"/",condition1name),xlab="log10(mean)",col="#BBBBBB10")
legend("topleft",c("Up","Down"),col=c("#3A3A9830","#83242430"),pch=c(20,20))
points(log10(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,"baseMean"]),dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,"log2FoldChange"],col="#3A3A9810",pch=20,cex=0.5,)
points(log10(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,"baseMean"]),dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,"log2FoldChange"],col="#83242410",pch=20,cex=0.5,)
abline(h=0)

plot(dbins.plus.vs.minus$log2FoldChange,-log2(dbins.plus.vs.minus$padj),pch=20,cex=0.5,xlab=paste0("log2 foldchange(",condition2name,"/",condition1name),ylab="-log2(FDR)",col="#BBBBBB14")
legend("topleft",c("Up","Down"),col=c("#3A3A9830","#83242430"),pch=c(20,20))
points(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,"log2FoldChange"],-log2(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange>0,"padj"]),col="#3A3A9830",pch=20,cex=0.5)
points(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,"log2FoldChange"],-log2(dbins.plus.vs.minus.filtered[dbins.plus.vs.minus.filtered$log2FoldChange<0,"padj"]),col="#83242430",pch=20,cex=0.5)
abline(v=0)
```

## Heatmap of accessibilities of Differntial Bins

```{r merge.dars, echo = F, message = F }
all.dbins <- rownames(dbins.plus.vs.minus.filtered)
tmpd<-assay(vsd[all.dbins,])
tmpd <- tmpd[,c(1,2,3,4,5,6)]
```

We have totally `r length(all.dbins)` differential bins, then we showed the accessibility difference (zscore over all conditions) in the heatmap and cluster the differential bins with hierarchical clustering (ward.D2 method in R). 

```{r HEATMAP, dev="png",dpi=300,fig.height=8,fig.width=8,echo=F,message=F }
pheatmap(tmpd, annotation_col=meta[,c("Group","Replicate")], fontsize_col = 6, fontsize_row = 4, cluster_cols=FALSE, show_colnames = F, show_rownames = F, clustering_method = "ward.D2", color = colorRampPalette(c("navyblue", "white" , "firebrick3"))(50), scale = "row")
```

## Summary of Differential Accessible Regions (DARs)

Next, we merge nearby differential bins (100bps each) into 'differential accessible regions'. We merge the opening bins and closing bins separately into opening DARs and closing DARs. Therefore, if a opening DAR is next to a closing DAR, they won't be merged into one.

```{r mergebin2region,echo=F}
MergeBin(dbin.plus.vs.minus.open.bed, dar.plus.vs.minus.open.bed)
MergeBin(dbin.plus.vs.minus.close.bed, dar.plus.vs.minus.close.bed)

dar.open <- readPeakFile(dar.plus.vs.minus.open.bed)
dar.close <- readPeakFile(dar.plus.vs.minus.close.bed)

```


## Genomic features of DARs

### Genomic distribution of DARs

DARs over the whole genome:
```{r dev="png",dpi=300,fig.height=24,fig.width=8,echo=F,message=F }
p.open <- covplot(dar.open, title="Openning DARs over Chromosomes") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.line.y = element_blank())
p.close <- covplot(dar.close, title="Closing DARs over Chromosomes") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.line.y = element_blank())
p.open/p.close
```

Summary of genomic feature distribution and distance to TSS distribution of opening DARs and closing DARs:

```{r dev="png",dpi=300,fig.height=8,fig.width=8,echo=F,message=F }

pfiles <- c(dar.plus.vs.minus.open.bed, dar.plus.vs.minus.close.bed)
names(pfiles) <- c("Opening DARs", "Closing DARs")

peakAnnoList <- lapply(pfiles, annotatePeak, TxDb=TxDb.Hsapiens.UCSC.hg38.knownGene, annoDb="org.Mm.eg.db", tssRegion=c(-3000, 3000), verbose=FALSE)

p1 <- plotAnnoBar(peakAnnoList)
p2 <- plotDistToTSS(peakAnnoList)
p1/p2

```

### Closing DARs under condition 2 `r condition2name` against condition 1 `r condition1name`

There are `r length(rownames(giggle.res.close))` Cistromes enriched (with at least 1 peak overlap and oddsratio>1) in DARs with descreasing accessibility in condition 2 compared with condition 1. The top 10 TFs by the Giggle score ranking are:

```{r echo=FALSE}
DT::datatable(giggle.res.close[order(-giggle.res.close$giggle_score),])
```

We can plot the odds-ratio in x-axis and pvalue (Fisher-test right tail test) in y-axis, while highlighting the top 10 Cistrome hits :

```{r dev="png",dpi=300,fig.height=8,fig.width=8,echo=F,message=F }
giggle.res.close.top10 <- giggle.res.close[order(giggle.res.close$giggle_score,decreasing = T),][1:10,]

t <- paste0(giggle.res.close.top10$biological_resource,collapse = "\n")
t <- paste0("Top10 result:\n",t)

p <- ggplot(data=giggle.res.close, aes(x=odds_ratio, y=fisher_right_tail, label=labels)) + geom_point() + xlim(0,5) + ylim(0,250)
p <- p + geom_label_repel(force=20, size=2, data = giggle.res.close.top10, max.overlaps = Inf) + xlab("Giggle log10 odds_ratio") + ylab("Giggle Fisher-test right-tail -log10 pvalue") + annotate(geom = 'text', label = t, x = Inf, y = -Inf, hjust = 1., vjust = -0.5)
p
```


### Cistrome hits of openning DARs vs closing DARs

We can combine cistrome hits associated with DARs with opening (increasing) and closing (decreasing) accessibilities. Top10 hits from either opening DARs or closing DARs results are highlighted.

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=8,echo=F,message=F }

giggle.combined <- merge(giggle.res.open, giggle.res.close, by="sample_id",all=T)[,c('sample_id','giggle_score.x','giggle_score.y')]
colnames(giggle.combined) <- c('sample_id','giggle_score.opening','giggle_score.closing')
giggle.combined[is.na(giggle.combined$giggle_score.opening),"giggle_score.opening"] <- 0
giggle.combined[is.na(giggle.combined$giggle_score.closing),"giggle_score.closing"] <- 0
giggle.combined <- merge(giggle.combined, ant, by.x="sample_id", by.y=0)

data.2 <- giggle.combined
data.2$factor <- ""
ix_label <- data.2$giggle_score.opening>=giggle.res.open.top10[10,]$giggle_score|data.2$giggle_score.closing>=giggle.res.close[10,]$giggle_score
data.2[ix_label,]$factor <- paste0(giggle.combined[ix_label,]$cellLine,":",giggle.combined[ix_label,]$factor)

p <- ggplot(data=data.2, aes(x=giggle_score.closing, y=giggle_score.opening, label=factor)) + geom_point(color = ifelse(data.2$factor == "","#99999930", "red"))
set.seed(10)
p <- p + geom_label_repel(force=10, size=3, max.overlaps = Inf) +xlab("Giggle score closing DARs") + ylab("Giggle score opening DARs")
p
```

## Enriched ENCODE cCRE (Candidate Cis-Regulatory Elements) analysis through GIGGLE

We checked the overlap between DARs and ENCODE phase 3 identified candidate cis-regulatory elements, and focused on the enhancer classes dELS ( distal Enhancer like Signature) and pELS ( promoter Enhancer like Signature).

```{r echo=FALSE, message=F, warning=F}
giggle.ccre.res.open <- RunGiggle.cCRE( dar.plus.vs.minus.open.bed, ccre.gigglepath )
giggle.ccre.res.close <- RunGiggle.cCRE( dar.plus.vs.minus.close.bed, ccre.gigglepath )
```

### Summary table

Summary of enrichment or depletion with cCRE annotations.

```{r echo=FALSE}
DT::datatable(giggle.ccre.res.open, caption = "ENCODE cCRE vs openning DARs")
```

```{r echo=FALSE}
DT::datatable(giggle.ccre.res.close, caption = "ENCODE cCRE vs closing DARs")
```

## Analysis of DAR Associated Genes (not using BETA)

We will first identify a set of genes of which the TSS is 'close to' the given DARs. 


```{r assoc.genes, include=FALSE, echo=FALSE}

# define nearby genes
peakAnnoDFs <- lapply(peakAnnoList, FUN = as.data.frame )
peakAnnoDFs <- lapply(peakAnnoDFs, FUN= function(x) {x[x$distanceToTSS<=dar2gene.distance.cutoff,]})
peakAnnoDFs.symbols <- lapply(peakAnnoDFs, FUN=function(x) {unique(x$SYMBOL)})
```
We use `r dar2gene.distance.cutoff` as a distance cutoff to identify those genes close to the DARs. We can identify `r length(unique(peakAnnoDFs$"Opening DARs"$SYMBOL))` genes close to opening DARs and `r length(unique(peakAnnoDFs$"Closing DARs"$SYMBOL))` genes close to closing DARs. 

```{r make.gene.list, include=FALSE, echo=FALSE}
set1.open <- bitr(unique(peakAnnoDFs$"Opening DARs"$SYMBOL), fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")
set2.close <- bitr(unique(peakAnnoDFs$"Closing DARs"$SYMBOL), fromType="SYMBOL", toType="ENTREZID", OrgDb="org.Mm.eg.db")

geneList <- list("Open"=set1.open, "Close"=set2.close)
```

### MSigDB Hallmark signatures

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=16,echo=F,message=F}
compH <- compareCluster(geneCluster = lapply(geneList, function(x){x$ENTREZID}), fun = "enricher", TERM2GENE = hgene, pvalueCutoff  = cp.pvalueCutoff, pAdjustMethod = cp.pAdjustMethod, minGSSize = cp.minGSSize, maxGSSize = cp.maxGSSize, qvalueCutoff = cp.qvalueCutoff )
dotplot(compH)

```

### MSigDB GO terms signatures

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=16,echo=F,message=F}
compGO <- compareCluster(geneCluster = lapply(geneList, function(x){x$ENTREZID}), fun = "enricher", TERM2GENE = gogene, pvalueCutoff  = cp.pvalueCutoff, pAdjustMethod = cp.pAdjustMethod, minGSSize = cp.minGSSize, maxGSSize = cp.maxGSSize, qvalueCutoff = cp.qvalueCutoff )
dotplot(compGO)

```

### MSigDB Oncogenic signatures

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=16,echo=F,message=F}
compONCO <- compareCluster(geneCluster = lapply(geneList, function(x){x$ENTREZID}), fun = "enricher", TERM2GENE = oncogene, pvalueCutoff  = cp.pvalueCutoff, pAdjustMethod = cp.pAdjustMethod, minGSSize = cp.minGSSize, maxGSSize = cp.maxGSSize, qvalueCutoff = cp.qvalueCutoff )
dotplot(compONCO)

```

### MSigDB TF targets signatures

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=16,echo=F,message=F}
compTFT <- compareCluster(geneCluster = lapply(geneList, function(x){x$ENTREZID}), fun = "enricher", TERM2GENE = tftgene, pvalueCutoff  = cp.pvalueCutoff, pAdjustMethod = cp.pAdjustMethod, minGSSize = cp.minGSSize, maxGSSize = cp.maxGSSize, qvalueCutoff = cp.qvalueCutoff )
dotplot(compTFT)

```

### MSigDB Canonical Pathways signatures

```{r echo=FALSE,dev="png",dpi=300,fig.height=8,fig.width=16,echo=F,message=F}
compCP <- compareCluster(geneCluster = lapply(geneList, function(x){x$ENTREZID}), fun = "enricher", TERM2GENE = pathgene, pvalueCutoff  = cp.pvalueCutoff, pAdjustMethod = cp.pAdjustMethod, minGSSize = cp.minGSSize, maxGSSize = cp.maxGSSize, qvalueCutoff = cp.qvalueCutoff )

dotplot(compCP)

```
